Kung Faux Pandas \\ \large Alternative Facts for Privacy Preservation

### 2018-05-07 paper/main.tex
Auto Update from local Sharelatex

While this pattern (workflow? combination?) makes it easy for readers to check source code for errors, it only enables reproducible research if the

Reproducing Machine learning requires access to source data
Source data is hard to get
In medical field, harder to get than most fields – IRBs, HIPAA regulation, etc.
Various methods used to synthesize or de-identify

A wide array of methods and techniques have been developed for generating synthetic data sas  data \cite{walonoski_synthea:_2018}

\bibliographystyle{unsrt}
\bibliography{bib}

>>>>

While this pattern (workflow? combination?) makes it easy for readers to check source code for errors, it only enables reproducible research if the 
\bibliographystyle{unsrt}
\bibliography{bib}
